\begin{abstract}[1]

In autonomous driving observing and evaluating the intentions of other traffic participants is one of the most crucial tasks to ensure safe trajectory planning and appropriate reactions. To be able to make proper judgments of future movement for other traffic participants, various variables must be considered, one of them is current and past positions of the objects of interest. Without proper prediction model, this is a very hard task to do. Usually, intentions are one variable which is not known, but it can be evaluated through partial observations and prior information about the behaviour of the object of interest.  Probabilistic models can be very beneficial in this scenario due to their capability to capture variance in motions. Therefore, this thesis presents a probabilistic approach for intention prediction based on trajectory data. To be able to predict motion intentions and direction future steps in trajectory, we propose a probabilistic intention prediction algorithm. During the algorithm training process, we modelled the initial probabilistic model from predefined movement demonstrations. The proposed algorithm was evaluated in a simulated driving environment and on data of a real car. In the simulated environment, two maps environments were used and prior knowledge, such us probabilities to go to one or another direction, which we have before starting to move. Prior information was incorporated into the algorithm regarding the particular map setting and prior demonstrations. As proof of concept, various experiments were done. They demonstrated that the proposed algorithm can correctly predict future movement intention ahead of the time: algorithm correctly predicts movements and further steps within $30-40$\% of testing trajectory, while the easiest recognizing movement to left direction. While testing an experimental setup with incorporated prior information, the algorithm predicts intentions much faster.\\


\end{abstract}
%
%
\selectlanguage{ngerman} % select german language
\begin{abstract}[2]
	
\textcolor{red}{TODO} 

\end{abstract}
\selectlanguage{english} % reset to english language
